%
% @author   Shmish  "shmish90@gmail.com"
% @legal    MIT     "(c) Christopher Schmitt"
%


\documentclass{article}


%
% Document Imports
%

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{tikz}



%
% Document Configuation
%

\newcommand{\hwAuthor}{Christopher Schmitt}
\newcommand{\hwSubject}{Math 218}
\newcommand{\hwSection}{Section 81}
\newcommand{\hwSemester}{Summer 2019}
\newcommand{\hwAssignment}{Assignment 8}


%
% Document Enviornments
%

\setlength{\headheight}{65pt}
\pagestyle{fancy}
\lhead{\hwAuthor}
\rhead{
  \hwSubject \\
  \hwSection \\
  \hwSemester \\
  \hwAssignment
}

\newenvironment{problem}[1]{
  \nobreak\section*{Problem #1}
}{}


%
% Document Start
%

\begin{document}
  \begin{problem}{1}
    Solve each of the following counting problems, writing your answer as an integer in the standard decimal notation.\par
    In how many ways can a student club that consists of 20 students select 3 students to attend a conference?
    $$\binom{20}{3} = 1140$$

    How many strings of 0s and 1s have length 11 and have exactly eight ones?
    $$\binom{11}{8} = 165$$

    How many strings of 0s and 1s have length 11 and have at most three ones?
    $$2^{11} - 2^{7} = 1920$$

    A donut shop has donuts in six different flavors: chocolate frosted, chocolate creme, glazed, jelly, plain, and Boston creme. The donut shop has an unlimited supply of each flavor. In how many different ways can the donut shop create a box of 18 donuts? Note that the box can include multiple donuts of the same flavor, and that donuts of the same flavor are considered indistinguishable.
    $$\binom{n + r - 1}{r} = \binom{6 + 18 - 1}{18} = \binom{23}{18} = 33649$$

    The donut shop now wants to create a box of 18 donuts, including at least four glazed ones. In how many ways can this be done?
    $$\binom{n + r - 1}{r} = \binom{6 + 14 - 1}{14} = \binom{19}{14} = 11628$$

    The donut shop now wants to create a box of 18 donuts, including at most four glazed ones. In how many ways can this be done?
    $$\binom{6 + 18 - 1}{18} - \binom{6 + 13 - 1}{13}= \binom{23}{18} - \binom{18}{13} = 33649 - 8568 = 25018$$

    The donut shop now wants to create a box of 18 donuts, including exactly four glazed ones. In how many ways can this be done?
    $$1 * \binom{5 + 14 - 1}{14} = \binom{18}{14} = 3060$$

    I want to buy one donut every day from Monday through Friday at the donut shop. In how many ways can this be done?
    $$\binom{n + r - 1}{r} = \binom{6 + 5 - 1}{5} = 252$$

    How many “words” can be formed by rearranging the letters of the word MATHEMATICALLY? The “words” do not have to be actual English words.
    $$\frac{14!}{2! * 3! * 2! * 2!} = 1816214400$$

    Find the coefficient of $x^8y^4$ in the expansion of the binomial $(x + 2y)^{12}$
    $$\binom{12}{4} = 495$$
    $$495(x^8)(2y^4) = 990x^8y^4$$
  \end{problem}

  \begin{problem}{2}
    $$(x + y)^{2k} = \sum_{i=0}^{2k} x^i y^{2k - 1} \binom{2k}{i}$$
    $$(x + y)^{2J + 1} = \sum_{i=0}^{2J + 1} x^i y^{2J} \binom{2J + 1}{i}$$
    Theorem: $$\sum_{0 \le i \le n, n\ odd} \binom{n}{i} = \sum_{0 \le i \le n, n\ even} \binom{n}{i}$$
    $$\sum \binom{2k+1}{i} = \sum \binom{2j}{i}$$
    $$?$$
  \end{problem}
\end{document}